Supporting Information:\\ NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-12-06 Manuscript/manuscriptPS.tex
Update text

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/structures.eps}
  \caption{\label{HGstructuresPSandPC}
    Overlayed snapshots from CHARMM36 simulations in best agreement with experiments
    to demonstrate the conformational fluctuations around
    (A) C$_\alpha$-C$_\beta$-C$_\gamma$-O$_\gamma$ and  O$_\alpha$-C$_\alpha$-C$_\beta$-N
    of PS headgroup and (B) N-C$_\beta$-C$_\alpha$-O$_\alpha$ and C$_\beta$-C$_\alpha$-O$_\alpha$-P
    dihedrals of PS and PC headgroups.
  }
  \todo{We need atom labeling for (B). Similar to the one in (A) would be good} \\
\end{figure}

@@

Calcium binding affinity to membranes containing negative charged PS lipids can be
measured by detecteding the PC lipid headgroup order parameters
from POPC:POPS (5:1) mixtures (section~\ref{electrometerFORmixtures}),
where the dehydrated lipid-ion complexes and phase separation are 
not observed~\cite{feigenson86,mattai89,roux90,roux91}.
Despite the lack of ion free reference state
in the presence of negatively charged lipids, the simulations give
coherent results for POPC headgroup order parameters as a function of
CaCl$_2$ in the POPC:POPS (5:1) mixtures (Fig. \ref{changesWITHCaClPS}).
As expected from the previous study of pure PC lipid
bilayers \cite{catte16}, almost all the tested simulation models overestimate the
experimentally observed~\cite{roux90} decrease of the POPC headgroup order parameters
in POPC:POPS (5:1) mixtures as a function of Ca$^{2+}$ concentration (Fig. \ref{changesWITHCaClPS}),
indicating overestimated calcium binding binding affinity.
Only exception is the CHARMM36 model with the NBfix
interaction employed for calcium~\cite{kim16}, which underestimates the changes in order parameter 
indicating weaker binding affinity than experiments.
%incorporated in the parameters give by the CHARMM-GUI at the time of running the simulations (January 2018),
Notably, CHARMM36 simulations with the NBfix corrections \cite{venable13,kim16} give similar binding affinities of
calcium and sodium to POPC bilayer (see section \ref{CHARMMcalciumNBfix}), in contrast to the experimental 
data~\cite{cevc90,akutsu81,altenbach84}. Therefore, we conclude that the calcium binding affinity,
manifested by the peaks in the density distributions along membrane normal (Fig. \ref{CAdensPCPSmixture}),
is underestimated in CHARMM36 simulations with the NBfix for calcium \cite{kim16} but overestimated 
in all the other tested models.

The headgroup order parameters of POPS measured from POPC:POPS (5:1) mixture
exhibit a strong dependence of CaCl$_2$ with small concentrations and rapid saturation
below 100 mM (Fig. \ref{changesWITHCaClPS}).
The order parameter of POPS $\beta$-carbon increase and the larger $\alpha$-carbon 
decrease with the added CaCl$_2$ in experiments. Slight increase is observed in
the smaller $\alpha$-carbon. All the changes are significantly overestimated in the
tested simulation models, including the CHARMM36 with the NBfix for calcium \cite{kim16},
where the binding affinity was underestimated. 
In addition, different simulation models predict qualitatively different behaviour
for the POPS $\alpha$-carbon order parameters with the added calcium.
For example, both order parameters decrease in Berger simulations but increase
in MacRog simulations, while behaviour in Lipid14/17 and CHARMM36 simulations is
more complicated. This is in contrast to the PC headgroup, where
qualitatively correct reponse to the bound ions is observed
in all simulation models despite of the significant discrepancies in the headgroup
structure without additional ions~\cite{catte16}. Therefore, we conclude that
the improvement of force fields is necessary to correctly describe interactions between
PS headgroup and calcium ions using MD simulations.
%The response of POPS headgroup order parameters to the bound charge is systematic but
%less well understood than the responce of PC headgroups used in the electrometer
%concept \cite{seelig87,roux90}.

>>>>

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/structures.eps}
  \caption{\label{HGstructuresPSandPC}
    Overlayed snapshots from CHARMM36 simulations in best agreement with experiments
    to demonstrate the conformational fluctuations around
    (A) C$_\alpha$-C$_\beta$-C$_\gamma$-O$_\gamma$ and  O$_\alpha$-C$_\alpha$-C$_\beta$-N
    of PS headgroup and (B) N-C$_\beta$-C$_\alpha$-O$_\alpha$ and C$_\beta$-C$_\alpha$-O$_\alpha$-P
    dihedrals of PS and PC headgroups.
    The CHARMM36 POPC simulation is from Ref. \citenum{POPCcharmm36T303K} and Slipids POPC from Ref. \citenum{POPCslipids298K}.
  }
  \todo{We need atom labeling for (B). Similar to the one in (A) would be good} \\
\end{figure}

@@

Calcium binding affinity to membranes containing negative charged PS lipids can be
measured by detecteding the PC lipid headgroup order parameters
from POPC:POPS (5:1) mixtures (section~\ref{electrometerFORmixtures}),
where the dehydrated lipid-ion complexes and phase separation are 
not observed~\cite{feigenson86,mattai89,roux90,roux91}.
Despite the lack of ion free reference state
in the presence of negatively charged lipids, the simulations give
coherent results for POPC headgroup order parameters as a function of
CaCl$_2$ in the POPC:POPS (5:1) mixtures (Fig. \ref{changesWITHCaClPS}).
As expected from the previous study of pure PC lipid
bilayers \cite{catte16}, almost all the tested simulation models overestimate the
experimentally observed~\cite{roux90} decrease of the POPC headgroup order parameters
in POPC:POPS (5:1) mixtures as a function of Ca$^{2+}$ concentration (Fig. \ref{changesWITHCaClPS}),
indicating overestimated calcium binding binding affinity.
Only exception is the CHARMM36 model with the NBfix
interaction employed for calcium~\cite{kim16}, which underestimates the changes in order parameter 
indicating weaker binding affinity than experiments.
%incorporated in the parameters give by the CHARMM-GUI at the time of running the simulations (January 2018),
Notably, CHARMM36 simulations with the NBfix corrections \cite{venable13,kim16} give similar binding affinities of
calcium and sodium to POPC bilayer (see section \ref{CHARMMcalciumNBfix}), in contrast to the experimental 
data~\cite{cevc90,akutsu81,altenbach84}. Therefore, we conclude that the calcium binding affinity
is underestimated in CHARMM36 simulations with the NBfix for calcium \cite{kim16} but overestimated 
in all the other tested models. This is evident in the calcium density distributions
along membrane normal where almost all Ca$^{2+}$ ions bind to the membrane interface in
all simulation models except CHARMM36 (Fig. \ref{CAdensPCPSmixture}).

The headgroup order parameters of POPS measured from POPC:POPS (5:1) mixture
exhibit a strong dependence of CaCl$_2$ with small concentrations and rapid saturation
below 100 mM (Fig. \ref{changesWITHCaClPS}).
The order parameter of POPS $\beta$-carbon increase and the larger $\alpha$-carbon 
decrease with the added CaCl$_2$ in experiments. Slight increase is observed in
the smaller $\alpha$-carbon. All the changes are significantly overestimated in the
tested simulation models, including the CHARMM36 with underestimated binding affinity.
In addition, different simulation models predict qualitatively different behaviour
for the POPS $\alpha$-carbon order parameters with the added calcium.
For example, both order parameters decrease in Berger simulations but increase
in MacRog simulations, while behaviour in Lipid14/17 and CHARMM36 simulations is
more complicated. This is in contrast to the PC headgroup, where
qualitatively correct reponse to the bound ions is observed
in all simulation models despite of the significant discrepancies in the headgroup
structure without additional ions~\cite{catte16}. Therefore, we conclude that
the improvement of force fields is necessary to correctly describe interactions between
PS headgroup and calcium ions in MD simulations.

### 2018-12-06 Manuscript/manuscriptPSsuppl.tex
Update text

\pagebreak
\section{Effect of the definition of concentration on the headgroup order parameters as a function of ion concentration.}\label{concentrationDEFsection}
Previous studies using the electrometer concept to assess the ion binding affinity to lipid
bilayers report ion concentrations either in water before solvating the lipids \cite{akutsu81,roux90,catte16}
or in bulk water after solvating the lipids \cite{altenbach84,melcr18}.
In this work, we use the former definition to be consistent with the reference
experimental data \cite{roux90}. The difference between these two concentrations increases
with the increasing ion binding affinity. However, the difference is essentially negligible
in the recent model \cite{melcr18} with realistic ion binding affinity (Fig. \ref{concentrationDEFfigure}).
\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/OP_ECC_POPC_DPPC_water_conc2_dppc_bulk.pdf}
  \caption{\label{concentrationDEFfigure}
    Difference between order parameter changes as a function of CaCl$_2$ concentration demonstrated
    for the two possible definitions of ion concentration, concentration in buffer before solvating the
    lipids (buffer concentration) and concentration in bulk after solvating the lipids (bulk concentration),
    from the recent model with realistic calcium binding affinity to a POPC bilayer \cite{melcr18}. 
}
\end{figure}

@@

Slices of the R-PDFL spectra (Fig. \ref{DPslices}) 
show a single splitting for the $\beta$-carbon with the order parameter value of 0.12,
and a superposition of a large and a very small splitting for the $\alpha$-carbon.
The larger splitting gives a order parameter value of 0.09, while the numerical value
from the small splitting cannot resolved with the available resolution.
\begin{figure}[]
%  \centering
  \includegraphics[width=20.0cm]{../Figs/SI_slices.pdf}
  \caption{\label{DPslices}
    Dipolar coupling slices from the R-PDFL experiment.
  }
  \todo{Labeling of carbons and explanations of numbers (chemical shift and order parameter) would be good.
  Also, the size of the figure in the file may not be optimal.}
\end{figure}

@@

The glycerol backbone order parameters of C$_2$ and C$_3$ from Slipids simulations
differ significantly from the other simulation results and experiments (Fig. \ref{HGorderParametersPS}),
as observed previously also for PC lipids \cite{botan15}.
The origin of this difference is more difficult to track without more elaborate analysis,
because different models show very complicated patterns of distinct structures
in the glycerol backbone region (Figs.~\ref{HGstructuresPS} and \ref{dihedralsHG}).

\begin{figure*}[]
  \centering
  \includegraphics[width=8.0cm]{../Figs/PS_Labels.png}
  \includegraphics[width=16.0cm]{../Figs/figS7.png}
  \caption{\label{dihedralsHG}
    Dihedral angle distributions of headgroup region of PS lipids from different simulation models.
  }
\end{figure*}

\begin{figure*}[]
  \centering
  \includegraphics[width=15.0cm]{../Figs/figS6.png}
  \caption{\label{dihedralsGLY}
    Dihedral angle distributions of glycerol backbone region of PS lipids from different simulation models.
  }
\end{figure*}

\begin{figure*}[]
  \centering
  \includegraphics[width=18.0cm]{../Figs/figS8.png}
  \caption{\label{HGandGLYstructuresPS}
    Overlayed snapshots from glycerol backbone and headgroup region from 
    different simulations of PS lipids.
  }
\end{figure*}

\begin{figure*}[]
  \centering
  \includegraphics[width=16.0cm]{../Figs/figS7PC.png}
  \caption{\label{dihedralsHGpc}
    Dihedral angle distributions of headgroup region of PS lipids from different simulation models.
  }
\end{figure*}

\begin{figure*}[]
  \centering
  \includegraphics[width=15.0cm]{../Figs/figS6PC.png}
  \caption{\label{dihedralsGLYpc}
    Dihedral angle distributions of glycerol backbone region of PS lipids from different simulation models.
  }
\end{figure*}

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/figS8_POPC.png}
  \caption{\label{HGandGLYstructuresPSPC}
    Overlayed snapshots from glycerol backbone and headgroup region from 
    different simulations of PS lipids.
  }
\end{figure}

@@

\section{Headgroup response to the additional counterions in POPC:POPS (5:1) mixtures}\label{mixtureTOadditionalCIs}
To evaluate counterion binding in different simulation models against experimental data~\cite{roux90},
we plot the headgroup order parameters measured from POPC:POPS 5:1 mixture
as a function of different monovalent ions added to the buffer (Fig. \ref{PSresponseTONaCl}). 
Experimental order parameters of POPC headgroup in the mixture are available as a function
of LiCl and KCl concentrations, while POPS headgroup order parameters are measured also
as a function of NaCl. Lithium interacts more strongly with PS headgroups than other monovalent 
ions~\cite{hauser83,hauser85,roux86,mattai89,roux90}, as also observed for PC headgroups~\cite{cevc90}. 
This is evident also in the changes of PS headgroup order parameters, which decrease with the addition of lithium 
but increase with the addition of sodium or potassium (Fig. \ref{PSresponseTONaCl}). 
POPC headgroup order parameters exhibit a clear decrease as a function of LiCl concentration
but only modest changes as a function of KCl concentration, indicating singificant 
Li$^+$ binding but only weak Na$^+$ binding to the mixture when interpreted using the
electrometer concept~\cite{akutsu81,altenbach84,seelig87}.

In simulations with Berger and CHARMM36 models, the responses of both headgroup order parameter
of POPC and the $\beta$ carbon of POPS to the added sodium or potassium are similar to the experiments
of LiCl (Fig. \ref{PSresponseTONaCl}), indicating overestimated binding affinity of the counterions 
in these simulations. The MacRog simulations with potassium exhibit weaker counterion binding affinity
(Fig. \ref{CIdensPSOCmixt}), but significantly larger error bars and
less systematic changes in the order parameters (Fig. \ref{PSresponseTONaCl}).
Similar unsystematic behaviour was also observed in the simulations of Lipid14/17 model
with the additional counterions \cite{POPCpopsLIPID17withKCI,POPCpopsLIPID17withK,POPCpopsLIPID17withNaCI,POPCpopsLIPID17withNa},
for which the data is not shown due to the formation of
ion clusters in water with relatively low (1 M) ion concentrations (Fig. \ref{ionCLUSTERS}).
Such clusters appering also in MagRog simulations with 4 M concentration of KCl
could explain the unsystematic changes of the order parameters in this model with the added KCl.
In conclusion, the results are in line with the section \ref{ciBINDINGsection}
in the main text, suggesting that the MacRog simulations with KCl give the most
realistic surface charge at the lipid bilayer interface.
\begin{figure*}[]
  \centering
  \includegraphics[width=17.0cm]{../Figs/CHANGESwithMONVALENTwithPS.eps}
  \caption{\label{PSresponseTONaCl}
    Changes of the PC (left) and PS (right) headgroup order parameters as a function of
    added NaCl, KCl and LiCl from POPC:POPS (5:1) mixture at 298~K
    (except Berger simulations are (4:1) mixture at 310~K).
    The experimental data is from Ref. \citenum{roux90}.
    The values from counterion-only systems are set as a zero point of y-axis.
    To correctly illustrate the significant forking of the $\alpha$-carbon order parameter
    in PS headgroup (bottom, right), the y-axis is tranferred with the same value for both order parameters such that the lower order
    parameter value is at zero.
  }
\end{figure*}
\begin{figure}[]
  \centering
  \includegraphics[width=8.0cm]{../Figs/CIdensPSOCmixt.eps}
  \caption{  Counterion density distributions from PC:PS mixtures.
\label{CIdensPSOCmixt}
  }
\end{figure}
\begin{figure}[]
  \centering
  \includegraphics[width=8.0cm]{../Figs/lipid17cluster.png}
  \includegraphics[width=8.0cm]{../Figs/MacRogIONcluster.png}
  \caption{Ion clusters appearing in POPC:POPS (5:1) lipid17/14 simulations with 1 M of NaCl (left)
    and MacRog simulations with 4 M of KCl (right).
\label{ionCLUSTERS}
  }
\end{figure}
\newpage

>>>>

\pagebreak
\section{Effect of the definition of concentration on the headgroup order parameters as a function of ion concentration.}\label{concentrationDEFsection}
Previous studies using the electrometer concept to assess the ion binding affinity to lipid
bilayers report ion concentrations either in water before solvating the lipids (buffer concentration) \cite{akutsu81,roux90,catte16}
or in bulk water after solvating the lipids (bulk concentration) \cite{altenbach84,melcr18}.
In this work, we use the former definition to be consistent with the reference
experimental data \cite{roux90}. The difference between these two concentrations increases
with the increasing ion binding affinity. However, the difference is essentially negligible
in the recent model \cite{melcr18} with realistic ion binding affinity (Fig. \ref{concentrationDEFfigure}).
\begin{figure}[]
  \centering
  \includegraphics[width=8.3cm]{../Figs/OP_ECC_POPC_DPPC_water_conc2_dppc_bulk.pdf}
  \caption{\label{concentrationDEFfigure}
    Changes of the headgroup order parameters as a function of CaCl$_2$ concentration using
    two possible definitions of ion concentration from the recent force field
    with realistic calcium binding affinity to a POPC bilayer \cite{melcr18}
    together with the experimental data \cite{akutsu81,altenbach84}. 
  }
\end{figure}

@@

Slices of the R-PDFL spectra (Fig. \ref{DPslices}) 
show a single splitting for the $\beta$-carbon with the order parameter value of 0.11,
and a superposition of a large and a very small splitting for the $\alpha$-carbon.
The larger splitting from the $\alpha$-carbon gives a order parameter value of 0.09, while the numerical value
from the small splitting cannot resolved with the available resolution.
\begin{figure}[]
%  \centering
  \includegraphics[width=20.0cm]{../Figs/SI_slices.pdf}
  \caption{\label{DPslices}
    Dipolar coupling slices from the R-PDFL experiment.
  }
  \todo{Labeling of carbons and explanations of numbers (chemical shift and order parameter) would be good.
    The splitting corresponding the larger $\alpha$-carbon order parameter should be also shown.
  Also, the size of the figure in the file may not be optimal.}
\end{figure}

@@

The dihedral angles and structures of the glycerol backbone and headgroup regions of POPS lipids show
wide variety between different simulation models (Figs. \ref{dihedralsHG}, \ref{dihedralsGLY} and \ref{HGandGLYstructuresPS}).
Detailed discussion of the structural differences is limited by the lack of realistic model that would correctly reproduce the
headgroup and glycerol backbone order parameters. However, some structural characteristics
of PS headgroup can be suggested based on the best available models
(Figs. \ref{dihedralsHGpc}, \ref{dihedralsGLYpc} and \ref{HGandGLYstructuresPSPC}), as discussed in the main text.
The glycerol backbone structures are not discussed in this works because our focus is on PS headgroup.
However, the data presented here can be useful for future investigations.
%backbone order parameters of C$_2$ and C$_3$ from Slipids simulations
%differ significantly from the other simulation results and experiments (Fig. \ref{HGorderParametersPS}),
%as observed previously also for PC lipids \cite{botan15}.
%The origin of this difference is more difficult to track without more elaborate analysis,
%because different models show very complicated patterns of distinct structures
%in the glycerol backbone region (Figs.~\ref{HGstructuresPS} and \ref{dihedralsHG}).

\begin{figure*}[]
  \centering
  \includegraphics[width=8.0cm]{../Figs/PS_Labels.png}
  \includegraphics[width=16.0cm]{../Figs/figS7.png}
  \caption{\label{dihedralsHG}
    Dihedral angle distributions of the headgroup region of POPS from different simulation models.
  }
\end{figure*}

\begin{figure*}[]
  \centering
    \includegraphics[width=8.0cm]{../Figs/PS_Labels.png}
  \includegraphics[width=13.0cm]{../Figs/figS6.png}
  \caption{\label{dihedralsGLY}
    Dihedral angle distributions of the glycerol backbone region of POPS lipids from different simulation models.
  }
\end{figure*}

\begin{figure*}[]
  \centering
  \includegraphics[width=18.0cm]{../Figs/figS8.png}
  \caption{\label{HGandGLYstructuresPS}
    Overlayed snapshots of the glycerol backbone and headgroup regions from different POPS simulations.
  }
\end{figure*}

\begin{figure*}[]
  \centering
  \includegraphics[width=16.0cm]{../Figs/figS7PC.png}
  \caption{\label{dihedralsHGpc}
    Dihedral angle distributions of the headgroup regions from CHARMM36 and Slipids simulations
    compared between the POPC and POPS lipids. 
    The CHARMM36 POPC simulation is from Ref. \citenum{POPCcharmm36T303K} and Slipids POPC from Ref. \citenum{POPCslipids298K}.
  }
\end{figure*}

\begin{figure*}[]
  \centering
  \includegraphics[width=15.0cm]{../Figs/figS6PC.png}
  \caption{\label{dihedralsGLYpc}
    Dihedral angle distributions of the glycerol backbone regions from CHARMM36 and Slipids simulations
    compared between the POPC and POPS lipids.
    The CHARMM36 POPC simulation is from Ref. \citenum{POPCcharmm36T303K} and Slipids POPC from Ref. \citenum{POPCslipids298K}.
  }
\end{figure*}

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/figS8_POPC.png}
  \caption{\label{HGandGLYstructuresPSPC}
    Overlayed snapshots of the headgroup and glycerol backbone regions 
    from CHARMM36 and Slipids simulations compared between the POPC and POPS lipids.
    The CHARMM36 POPC simulation is from Ref. \citenum{POPCcharmm36T303K} and Slipids POPC from Ref. \citenum{POPCslipids298K}.
  }
\end{figure}

@@

\section{Headgroup response to the additional counterions in POPC:POPS (5:1) mixtures}\label{mixtureTOadditionalCIs}
To evaluate counterion binding in different simulation models against experimental data~\cite{roux90},
we plot the headgroup order parameters measured from POPC:POPS 5:1 mixture
as a function of different monovalent ions added to the buffer (Fig. \ref{PSresponseTONaCl}). 
Experimental order parameters of POPC headgroup in the mixture are available as a function
of LiCl and KCl concentrations, while POPS headgroup order parameters are measured also
as a function of NaCl. Lithium interacts more strongly with PS headgroups than other monovalent 
ions~\cite{hauser83,hauser85,roux86,mattai89,roux90}, as also observed for PC headgroups~\cite{cevc90}. 
The different binding behaviour is evident also in the changes of PS headgroup order parameters, which decrease with the addition of lithium 
but increase with the addition of sodium or potassium (Fig. \ref{PSresponseTONaCl}). 
POPC headgroup order parameters exhibit a clear decrease as a function of LiCl concentration
but only modest changes as a function of KCl concentration, indicating singificant 
Li$^+$ binding but only weak K$^+$ binding to the mixture when interpreted using the
electrometer concept~\cite{akutsu81,altenbach84,seelig87}.

In simulations with Berger and CHARMM36 models, the responses of headgroup order parameter
of both POPC and POPS to the added sodium or potassium are more similar to the experiments
with LiCl (Fig. \ref{PSresponseTONaCl}), indicating overestimated binding affinity of sodium and potassium 
in these simulations. The MacRog simulations with potassium exhibit weaker counterion binding affinity
(Fig. \ref{CIdensPSOCmixt}), but significantly larger error bars and
less systematic changes in the order parameters (Fig. \ref{PSresponseTONaCl}).
Similar unsystematic behaviour was also observed in the simulations of Lipid14/17 model
with the additional counterions \cite{POPCpopsLIPID17withKCI,POPCpopsLIPID17withK,POPCpopsLIPID17withNaCI,POPCpopsLIPID17withNa},
for which the data is not shown due to the formation of
ion clusters in water with relatively low (1 M) ion concentrations (Fig. \ref{ionCLUSTERS}).
Appearance of such clusters also in the MagRog simulations with 4 M concentration of KCl
could explain the unsystematic changes of the order parameters in this model with the added KCl.
In conclusion, the results are in line with the section \ref{ciBINDINGsection}
in the main text, suggesting that the MacRog simulations with KCl give the most
realistic surface charge at the lipid bilayer interface among the tested simulation models.
\begin{figure*}[]
  \centering
  \includegraphics[width=17.0cm]{../Figs/CHANGESwithMONVALENTwithPS.eps}
  \caption{\label{PSresponseTONaCl}
    Changes of the PC (left) and PS (right) headgroup order parameters as a function of
    added NaCl, KCl and LiCl from POPC:POPS (5:1) mixture at 298~K
    (except Berger simulations are (4:1) mixture at 310~K).
    The experimental data is from Ref. \citenum{roux90}.
    The values from counterion-only systems are set as a zero point of y-axis.
    To correctly illustrate the significant forking of the $\alpha$-carbon order parameter
    in PS headgroup (bottom, right), the y-axis is tranferred with the same value for both order parameters such that the lower order
    parameter value is at zero.
  }
\end{figure*}
\begin{figure}[]
  \centering
  \includegraphics[width=8.0cm]{../Figs/CIdensPSOCmixt.eps}
  \caption{  Counterion density distributions from PC:PS mixtures.
\label{CIdensPSOCmixt}
  }
\end{figure}
\begin{figure}[]
  \centering
  \includegraphics[width=8.0cm]{../Figs/lipid17cluster.png}
  \includegraphics[width=8.0cm]{../Figs/MacRogIONcluster.png}
  \caption{Ion clusters appearing in POPC:POPS (5:1) lipid17/14 simulations with 1 M of NaCl (left)
    and MacRog simulations with 4 M of KCl (right).
\label{ionCLUSTERS}
  }
\end{figure}
\newpage
